---
title: "Johan Ibrahim's CV"
author: Dr Johan Ibrahim
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'custom.css', 'resume']
    self_contained: true
---
<!-- inicio academic icons -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">

<!-- final academic icons -->
 
<!-- start font awesome -->
<script src="https://kit.fontawesome.com/e82584e357.js" crossorigin="anonymous"></script>

 
<!-- final font awesome -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1_Y3HPpenl9Q0rovGZUmto6kxSCrtv8BsTGSfdk-xdXk/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume == TRUE)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
=================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```


```{r}
if(params$pdf_mode){
  cat("View this CV online at drjohan.github.io/johancvcra/index.html")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/DrJohan/johancvcra/raw/main/drjohan_cv.pdf).")
}
```

Contact {#contact}
--------------------------------------------------------------------------------
- <i class="fa fa-envelope"></i> johan@ms.rcsiucd.edu.my
- <i class="fab fa-linkedin-in"></i>  [Johan_Ibrahim](http://linkedin.com/in/johan_ibrahim)
- <i class="fa-brands fa-whatsapp"></i> +60126466545

Research Skills {#skills}
---------------------------------------------------------------------------------

- ICH-GCP
- Clinical Trial Management
- Site Management
- Infectious Disease Modelling
- Scientific Literature Review
- Experimental Design and Analysis
- Artificial Intelligence

Skills {#skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skill_bars()
```


Main
================================================================================

Dr Johan Ibrahim {#title}
--------------------------------------------------------------------------------

Hi!! My name is Johan Ibrahim. Currently I'm working as Clinical Research Associate with [Aesculape CRO Belgium-Singapore](https://www.aesculape.com). 


I describe myself as dedicated, highly motivated and enthusiastic medical graduate with in-depth knowledge of research design and methodologies, medical statistic, big data capture, curation, manipulation and visualization and has been certified Good Clinical Practice researcher from National Institute of Health (NIH) Malaysia.Able to use own initiative and work as part of a team under pressure to meet challenging deadlines/objectives. 

Work Experience {data-icon=suitcase}
--------------------------------------------------------------------------------
::: aside

:::

```{r}
CV %<>% print_section('working_experience')
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```


Selected Short Courses Attended {data-icon=book} 
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('short_courses')
```
<br>
<br>
<br>
<br>
<br>
<br>
<br>


Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------
::: aside
I'm a medical doctor by training. In the past, I've served people in Indonesia and Malaysia and actively involve in search and rescue during Earthquake in Indonesia, 2006. Then, I decided to have a change in career after being inspired by my mentor Prof Ronan Conroy and decided to pursue a career in research as medical statistician cum data scientist. 

I'm an active participant in the local R community [Malaysia R User Group](https://www.meetup.com/MY-RUserGroup/). I'm also one of the moderator in [Analisa Data Dengan R Studio group](https://www.facebook.com/groups/R4data) and actively giving guidance for RStudio beginner.

:::





```{r}
CV %<>% print_section('research_projects')
```


Selected Events Attended {data-icon=calendar-check}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('events_attended')
```


<!-- Selected Data Science Writing {data-icon=chart-line} -->
<!-- -------------------------------------------------------------------------------- -->

::: aside

The source code is available <i class="fa fa-github"></i> [Github](https://github.com/DrJohan/johancvcra).
Last updated on `r Sys.Date()`. The most recent version of this CV is [available here](drjohan.github.io/johancvcra/index.html)

:::


